Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
wordings

The digital controllers synthesised in this paper are typically used in
closed loops with continuous (and physical) plants.  Thus, the proposed
approach has to consider dynamics of continuous parts of system ({\it e.g.},
plant) and discrete parts ({\it e.g.}, digital controller).

For this purpose, the design procedure is based on a discretised model for a
continuous plant.  Considering only transfer function models, we are
interested in a $z$-domain transfer function that considers all the aspects
about the continuous plant (with a Laplace domain transfer function $G(s)$) and the sampling and hold process.

Note that $G(z)$ is a discrete model of a real (and continuous) plant, i.e.,
a continuous model of the plant must be discretised to obtain the discrete
equivalent coefficients via ZOH discretisation.

@@

Although there are several discretisation methods available in the
literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
more suitable for representing the sample and hold processes that are
typically employed in complex systems~\cite{istepanian2012digital}, {\it
i.e.}, the ZOH discretisation models the exact effect of sampling and DAC
interpolation over the plant.

\begin{myassumption}
%
The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it
i.e.}, there is no delay between sampling the plant output at ADC and
updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
%
\end{myassumption}

@@

The lemma \ref{eq:pulsetf} is ensures the poles and zeros matching with $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$ operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is sufficient for the stability studies over $G(s)$

>>>>

The digital controllers synthesised using the algorithm we present in this
paper are typically used in closed loops with continuous (and physical)
plants.  Thus, the proposed approach has to consider dynamics of continuous
parts of the system (i.e., the plant) and the discrete parts (i.e., the
digital controller).  To obtain a joint model, the discretise the continuous
plant.  We only consider transfer function models, and require a $z$-domain
transfer function that captures all aspects of the continuous plant (with a
Laplace domain transfer function $G(s)$) and the sampling and hold process.

Note that $G(z)$ is a discrete model of a real-domain (and continuous)
plant, i.e., the continuous model of the plant must be discretised to obtain
the discrete equivalent coefficients via ZOH discretisation.

@@

Although there are several discretisation methods available in the
literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
more suitable for representing the sample and hold processes that are
typically employed in complex systems~\cite{istepanian2012digital}, i.e.,
the ZOH discretisation models the exact effect of sampling and DAC
interpolation over the plant.

\begin{myassumption}
%
The Sample and Hold of the ADC and the ZOH of the DAC are synchronized,
i.e., there is no delay between sampling the plant output at ADC and
updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
%
\end{myassumption}

@@

Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching with
$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is
sufficient for the stability studies over $G(s)$.
